% -----------------------------------------------------------------------------
% The MIT License (MIT)
%
% Copyright (c) 2015 Pejman Ghorbanzade
%
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the "Software"), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
%
% The above copyright notice and this permission notice shall be included in
% all copies or substantial portions of the Software.
%
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
% THE SOFTWARE.
% -----------------------------------------------------------------------------

\section*{Question 1}
The following programs have each a \textbf{single} compilation error given below. You are expected to find and fix the error so that given command-line arguments will lead to expected output as indicated.

\begin{enumerate}[label=\textbf{(\alph*)}]

\item Execution Script \hfill Expected Output\\
\texttt{java HelloWorld President} \hfill \texttt{Hello President!}
\begin{lstlisting}
public class HelloWorld {
	public static void main(String[] args) {
		System.out.println("Hello + args[0] + "!");
	}
}
\end{lstlisting}

\begin{terminal}
HelloWorld.java:3: error: ')' expected
    System.out.println("Hello + args[0] + "!");
HelloWorld.java:3: error: unclosed string literal
    System.out.println("Hello + args[0] + "!");
HelloWorld.java:3: error: ';' expected
    System.out.println("Hello + args[0] + "!");
HelloWorld.java:5: error: reached end of file while parsing
}
4 errors
\end{terminal}

\newpage

\item Execution Script \hfill Expected Output\\
\texttt{java Feet2Centimeters 5} \hfill \texttt{152.4}
\begin{lstlisting}
public class Feet2Centimeters {
	public static void main(String[] args) {
		double conversion = 30.48;
		double cm = args[0] * conversion;
		System.out.println(cm);
	}
}
\end{lstlisting}

\begin{terminal}
Feet2Centimeters.java:4: error: bad operand types for binary operator '*'
        double cm = args[0] * conversion;
1 error
\end{terminal}

\item Execution Script \hfill Expected Output\\
\texttt{java SphereSurface 7} \hfill \texttt{615.75}

\begin{lstlisting}
public class SphereSurface {
	public static void main(String[] args) {
		double radius = Double.parseDouble(args[0]);
		double surface = 4 * Math.PI * pow(radius, 2);
		System.out.printf("%.2f\n", surface);
	}
}
\end{lstlisting}

\begin{terminal}
SphereSurface.java:4: error: cannot find symbol
        double surface = 4 * Math.PI * pow(radius, 2);
1 error
\end{terminal}

\newpage

\item Execution Script \hfill Expected Output\\
\texttt{java Factorial 5} \hfill \texttt{120}

\begin{lstlisting}
public class Factorial {
	public static void main(String[] args) {
		int num = Integer.parseInt(args[0]);
		int counter = 1;
		int result = 1;
		do
			result *= counter;
			counter++;
		while (counter <= num);
		System.out.println(result);
	}
}
\end{lstlisting}

\begin{terminal}
Factorial.java:7: error: while expected
	result *= counter;
Factorial.java:8: error: illegal start of expression
	counter++;
Factorial.java:8: error: ';' expected
	counter++;
Factorial.java:9: error: not a statement
	while (counter <= num);
4 errors
\end{terminal}

\end{enumerate}

\newpage

\section*{Question 2}
The following code snippet had been written on a scrap of paper found in a trashcan of a classroom.
The program is error-free and functions as expected but unfortunately no one knows what it does.
Read the code snippet and explain how it works.
No assumption can be made about user input except that the input is always an integer.

\begin{lstlisting}
import java.util.Scanner;
public class FiveStar {
	public static void main(String[] args) {
		Scanner key = new Scanner(System.in);
		System.out.printf("Insert Number: ");
		int num = key.nextInt();
		int rand = (int) (Math.random() * 100) + 1;
		double result = num * Math.pow(1, rand);
		double sum = 0;
		int var = 0;
		while (var != 6) {
			sum += Math.pow(-1, var) * result;
			var++;
		}
		System.out.printf("Result is %.2f\n", sum);
	}
}
\end{lstlisting}

\newpage

\section*{Question 3}
Write a program \texttt{NumberLimit.java} that prompts user for a strictly positive integer number $x$ and prints the largest non-negative integer number $y$ such that $y^3 < x$.
For simplicity, assume the user input is always a strictly positive integer number.
Following is an expected sample run of your program.

\begin{terminal}
$ javac NumberLimit.java
$ java NumberLimit
Upper Limit? 70
Number is 4.
\end{terminal}
