% -----------------------------------------------------------------------------
% The MIT License (MIT)
%
% Copyright (c) 2015 Pejman Ghorbanzade
%
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the "Software"), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
%
% The above copyright notice and this permission notice shall be included in
% all copies or substantial portions of the Software.
%
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
% THE SOFTWARE.
% -----------------------------------------------------------------------------

\def \topDirectory {..}

\documentclass[12pt,letterpaper,twoside]{article}
\usepackage{\topDirectory/template/style/directives}
\usepackage{\topDirectory/template/style/assignment}
\input{\topDirectory/template/config}
\setlist{leftmargin=10pt, itemsep=0pt, parsep=0pt}

\begin{document}

\doc{title}{Course Syllabus}
\doc{points}{0}

\prepare{header}

\subsection*{Objectives}
Students will obtain a thorough understanding of object oriented paradaigm and its fundamentals and will be able to incorporate them for solving simple computing problems using Java programming language.

\subsection*{Topics}
\begin{itemize}
\item[] Introduction to Java Programming Language
\item[] Fundamentals of Programming
\item[] Object-Oriented Programming
\item[] Object-Oriented Design
\item[] Basic Data Structures
\end{itemize}

\subsection*{Prerequisites}
Students taking this course should have passed or be taking one of Math129 or Math130 courses.

\subsection*{Venue}
\begin{itemize}
\item[] Classroom: M-01-213
\item[] Weekdays: Monday, Wednesday
\item[] Time: 17:30 - 18:45
\end{itemize}

\subsection*{Instructor}
\begin{itemize}
\item[] Pejman Ghorbanzade
\item[] Mail Address: \texttt{mail@ghorbanzade.com}
\item[] Office: S-3-124
\item[] Office Hours: Mondays, Wednesdays 16:00 to 17:30
\end{itemize}

\subsection*{Teaching Assistants}
\begin{itemize}
\item[] Siyu Peng
\item[] Mail Address: \texttt{siyu.peng001@umb.edu}
\end{itemize}

\subsection*{Grading}
\begin{itemize}
\item[] Homeworks: 40 points
\item[] Midterm Exam: 20 points
\item[] Final Exam: 40 points
\end{itemize}

\subsection*{Important Dates}
\begin{itemize}
\item[] First Lecture: Sep 09, 2015
\item[] Midterm Exam: Oct 14, 2015
\item[] Last Lecture: Dec 14, 2015
\item[] Final Exam: To be determined.
\end{itemize}

\subsection*{Recommended Textbook}
Y. Daniel Liang, \textit{Introduction to Java Programming}, 10th Edition, Prentice Hall, 2014.

\subsection*{Attendance Policy}
Lecture and lab attendance is optional but strongly encouraged. Students are strongly advised to attend both. Slides do not reﬂect all materials covered in lectures. Students are responsible for material covered in any class that they do not attend. Students are also expected to check this website regularly for latest announcements, upcoming events and released homeworks.

\subsection*{Late Submission Policy}
Homeworks may be submitted late by up to two days; the penalty for late submission increasing linearly from 20\% to 100\% of the homework score.

\subsection*{Makeup Policy}
Unless a good reason and its supporting evidence are given - e.g. due to illness or emergency events - no makeup is acceptable for students missing a homework assignment or an exam.

\subsection*{Accomodations}
Section 504 of the Americans with Disabilities Act of 1990 offers guidelines for curriculum modifications and adaptations for students with documented disabilities. If applicable, students may obtain adaptation recommendations from the \href{http://www.umb.edu/academics/vpass/disability}{Ross Center for Disability Services}, M-1-401, (617-287-7430). The student must present these recommendations and discuss them with each professor within a reasonable period, preferably by the end of Drop/Add period.

\subsection*{Student Conduct}
Students are required to adhere to the University Policy on Academic Standards and Cheating, to the University Statement on Plagiarism and the Documentation of Written Work, and to the \href{http://www.umb.edu/life_on_campus/policies/community/code}{Code of Student Conduct} as delineated in the catalog of Undergraduate Programs, pp. 44-45, and 48-52.

\end{document}
