%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CS114: Introduction to Programming in Java
% Copyright 2015 Pejman Ghorbanzade <mail@ghorbanzade.com>
% Creative Commons Attribution-ShareAlike 4.0 International License
% https://github.com/ghorbanzade/UMB-CS114-2015F/blob/master/LICENSE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def \topDirectory {../..}
\def \texDirectory {\topDirectory/src/main/tex}

\documentclass[10pt, compress]{beamer}

\usepackage{\texDirectory/template/style/directives}
\input{\texDirectory/template/config}
\usepackage{\texDirectory/template/style/beamerthemeUmassLecture}
\doc{number}{1}
%\setbeamertemplate{footline}[text line]{}

\begin{document}
\prepareCover

\section{Course Administration}

\begin{slide}
	\begin{block}{Lecture Venue}
		Mondays and Wednesdays, 5:30 PM to 6:45 PM\\
		McCormack Building, 1st Floor, Room No. 213\\
		University of Massachusetts Boston
	\end{block}
\end{slide}

\begin{slide}
	\begin{block}{Instructor}
		Pejman Ghorbanzade\\\href{mailto:mail@ghorbanzade.com}{(mail [at] ghorbanzade [dot] com)}

		\textbf{Office}\\S-3-124B (Network Information Systems Laboratory)

		\textbf{Office Hours}\\Mondays, Wednesdays 4:00 PM -- 5:30 PM

		\textbf{Phone}\\617-287-6419
	\end{block}
\end{slide}

\begin{slide}
	\begin{block}{Teaching Assistant}
		Azib Hassan\\\href{mailto:azib.hassan001@umb.edu}{azib.hassan001 [at] umb [dot] edu}
	\end{block}
\end{slide}

\begin{slide}
	\begin{block}{Course Website}
		Students are advised to check \href{http://www.ghorbanzade.com/teaching/UMB-CS114-2015F}{\alert{Course Website}} regularly for announcements, assignments, learning materials and forum discussions.
	\end{block}
\end{slide}

\begin{slide}
	\begin{block}{Textbook}
		\begin{itemize}
			\item[] Y. Daniel Liang, \emph{Introduction to Java Programming}, 10th edition, Prentice Hall, 2014.
		\end{itemize}
		Textbook is recommended but not required.

		Lectures will cover topics in the textbook and beyond.

		A list of useful resources are posted on course website.
	\end{block}
\end{slide}

\begin{slide}
	\begin{block}{Prerequisites}
		Students taking this course should have passed or be taking one of Math129 or Math130 courses.

		Previous computer programming skills are not required.

		Creative mind is a must.
	\end{block}
\end{slide}

\begin{slide}
	\begin{block}{Grading}
		\begin{itemize}
			\item[-] Assignments (40 points)\\5 assignments each 8 points
			\item[-] Midterm Exam (20 points)
			\item[-] Final Exam (40 points)
		\end{itemize}
	\end{block}
\end{slide}

\begin{slide}
	\begin{block}{Policies}
		Attendance is optional but strongly encouraged. Homeworks are released online through the course website. Solutions must be submitted online through the course website.

		Slides do not reflect all materials covered in lectures.

		University policies on academic standards and cheating, plagiarism and documentation of written work and code of student conduct are strictly enforced.
	\end{block}
\end{slide}

\begin{slide}
	\begin{block}{Tips and Tricks}
		\begin{itemize}
			\item[] Prepare yourself by thinking ahead.
			\item[] Get your hands dirty. Code during lectures.
			\item[] Start assignments the day they are posted.
			\item[] Explore different programming languages.
			\item[] Marry Google. Make friends with Wikipedia.
			\item[] Explore Different Editors.
		\end{itemize}
	\end{block}
\end{slide}

\plain{}{Keep Calm\\and\\Love Programming}

\end{document}
