%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CS114: Introduction to Programming in Java
% Copyright 2015 Pejman Ghorbanzade <mail@ghorbanzade.com>
% Creative Commons Attribution-ShareAlike 4.0 International License
% https://github.com/ghorbanzade/UMB-CS114-2015F/blob/master/LICENSE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def \topDirectory {../..}
\def \texDirectory {\topDirectory/src/main/tex}

\documentclass[10pt, compress]{beamer}

\usepackage{\texDirectory/template/style/directives}
\input{\texDirectory/template/config}
\usepackage{\texDirectory/template/style/beamerthemeUmassLecture}
\doc{number}{5}
%\setbeamertemplate{footline}[text line]{}

\begin{document}
\prepareCover

\section{Course Administration}

\begin{slide}
	\begin{itemize}
		\item[] 36/40 user accounts at \href{http://www.ghorbanzade.com}{Course Website} created so far.
		\item[] Solutions to assignments should be submitted online via \href{http://www.ghorbanzade.com}{Course Website}.
	\end{itemize}
\end{slide}

\begin{slide}
	\begin{block}{Overview}
		\begin{itemize}
			\item[] Class PrintStream
			\item[] Class String
		\end{itemize}
	\end{block}
\end{slide}

\section{Class PrintStream}

\begin{slide}
	\begin{block}{HelloWorld.java}
		\begin{minted}[fontsize=\small,tabsize=8]{java}
			public class HelloWorld {
			    public static void main(String[] args) {
			        System.out.println("Hello World!");
			        System.out.print("Hello World!\n");
			        System.out.printf("Hello %s!\n","World");
			    }
			}
		\end{minted}
	\end{block}
\end{slide}

\begin{slide}
	String is not a primitive data type. Yet, String concatenation operation is a built-in Java feature.
	\begin{block}{HelloStudents.java}
	\begin{minted}[fontsize=\small,tabsize=8]{java}
		public class HelloStudents {
		    public static void main(String[] args) {
		        System.out.println("Hello CS110 Students!");
		        System.out.println("Hello " + "CS110" + " Students!");
		        int code = 110;
		        System.out.println("Hello CS" + code + " Students!");
		        String message = "Hello CS110 Students!";
		        System.out.println(message);
		    }
		}
	\end{minted}
	\end{block}
\end{slide}

\begin{slide}
	\begin{block}{PrintStream}
		PrintStream is a built-in class in java.io package. It contains pre-defined methods and one field (out) to print computer output.
	\end{block}
	\begin{block}{System.out.println()}
		\begin{itemize}
			\item[] \texttt{System} is a built-in class in java.lang package. It contains pre-defined methods and fields.
			\item[] \texttt{out} is a field in System class and a reference of PrintStream class.
			\item[] \texttt{println()} is a method of Printstream class.
		\end{itemize}
	\end{block}
\end{slide}

\begin{slide}
	println() is not the only method of PrintStream class.
	\begin{block}{HelloUniverse.java}
	\begin{minted}[fontsize=\small,tabsize=8]{java}
		public class HelloUniverse {
		    public static void main(String[] args) {
		        System.out.print("Hello \'Universe\'!\n");
		        System.out.print("Hello " + "\"Univer" + "se\"!\n");
		        System.out.print("Hello \t Universe!");
		        System.out.print("Hello \n Universe!\n");
		    }
		}
	\end{minted}
	\end{block}
\end{slide}

\begin{slide}
	printf() is a more powerful method of PrintStream class.
	\begin{block}{HelloNumber.java}
	\begin{minted}[fontsize=\small,tabsize=8]{java}
		public class HelloNumber {
		    public static void main(String[] args) {
		        double num = 142.2567;
		        System.out.printf("Hello " + num + "!\n");
		        System.out.printf("Hello %f!\n", num);
		        System.out.printf("Hello %4.2f!\n", num);
		        System.out.printf("Hello %08.f!", num);
		    }
		}
	\end{minted}
	\end{block}
\end{slide}

\section{Class String}

\begin{slide}
	String is a class and a built-in data type. It provides methods to modify, handle or analyze string literals. Every string literal is an instance (object) of class String.
	\begin{block}{Methods}
		\begin{columns}
			\begin{column}{0.5\textwidth}
				\begin{itemize}
					\item[] length()
					\item[] trim()
					\item[] startsWith()
					\item[] endsWith()
					\item[] charAt()
					\item[] indexOf()
					\item[] lastIndexOf()
				\end{itemize}
			\end{column}
			\begin{column}{0.5\textwidth}
				\begin{itemize}
					\item[] equals()
					\item[] equalsIgnoreCase()
					\item[] compareTo()
					\item[] compareToIgnoreCase()
					\item[] contains()
					\item[] concat()
					\item[] substring()
				\end{itemize}
			\end{column}
		\end{columns}
	\end{block}
\end{slide}

\begin{slide}
	\begin{block}{Methods (cont'd)}
		\begin{columns}
			\begin{column}{0.5\textwidth}
				\begin{itemize}
					\item[] isEmpty()
					\item[] toUpperCase()
					\item[] toLowerCase()
					\item[] join()
					\item[] match()
				\end{itemize}
			\end{column}
			\begin{column}{0.5\textwidth}
				\begin{itemize}
					\item[] valueOf()
					\item[] format()
					\item[] split()
					\item[] replace()
				\end{itemize}
			\end{column}
		\end{columns}
	\end{block}
	\begin{block}{Remember}
		String literals are objects. It is not a good idea to compare them with ={}= relational operator. It is wise to use equals() method instead.
	\end{block}
\end{slide}

\plain{}{Keep Calm\\and\\Practice}

\end{document}
